Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-23 krs-survey.tex
Filled section on symbol grounding

>>>>

\emph{Grounding} (also called \emph{anchoring} when specifically refering to
building links between \emph{percepts} and \emph{physical
objects}~\cite{Coradeschi2003}) is the task consisting in building and
maintaining a bi-directional link between sub-symbolic representations (sensors
data, low-level actuation) and symbolic represtentations that can be
manipulated and reasoned about~\cite{Harnad1990}.

Being embodied entities with interaction with other embodied entities as a
fundamental requirement, robots and robotic is deeply concerned by the
grounding issue.

Being actually implemented on real service robots, all the symbolic knowledge
representation systems that we review in this study have some kind of grounding
process. Numerous approaches exist, like amodal
\emph{proxies}~\cite{Jacobsson2008}, grounded amodal
representations~\cite{Alami2011, Mavridis2006} or semantic maps
(Figure~\ref{fig|semanticmap}, \cite{Nuechter2008, Galindo2008,Blodow2011}).

\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{semanticmaps_hertzberg.png}
    \caption{Example of a semantic map, taken from~\cite{Nuechter2008}.}
    \label{fig|semanticmap}
\end{figure}
